07_topconfects

### 2019-08-14 analysis/07_topconfects.Rmd
small change

```{r setup, message=F, comment=FALSE, warning=FALSE, results='hide'}
library(DESeq2)
library(topconfects)
library(tidyverse)

@@

@@

```{r subsetnconfects}
subsetnconfects <- function(mygroup, mytreatments, mycomparison){
  # subset col and count data
  colData <- c.colData %>%
      dplyr::filter(sextissue == mygroup) %>%
      dplyr::filter(treatment %in% mytreatments) %>%
      droplevels()
  row.names(colData) <- colData$V1

>>>>

```{r setup, message=F, comment=FALSE, warning=FALSE, results='hide'}
library(DESeq2)
library(tidyverse)
library(topconfects)

@@

#deseq2_confects(dds, name="group_A_vs_B", step=0.1) # Error: subscript contains invalid names

@@

```{r subsetnconfects2}

subsetnconfects <- function(mygroup, mytreatments, mycomparison){
  # subset col and count data
  colData <- c.colData %>%
      dplyr::filter(sextissue == mygroup) %>%
      dplyr::filter(treatment %in% mytreatments) %>%
      droplevels()
  row.names(colData) <- colData$V1
